{Good covers and algebras on conically smooth spaces}

### 2025-09-02 paperversion/paper.tex
more localities

\documentclass[]{amsart}

@@

\begin{lemma}
    Let $X$ be a smooth manifold with corners and let $I^+\colon\R_{\geq0}\times \partial(\R_{\geq0}\times\partial X)\hookrightarrow\R_{\geq0}\times X$ be as in \Cref{O6BEXS3}. Then 
    \[
        I^+=\alpha_I\circ\phi
    \]
    where $\alpha_I$ is as in \Cref{K52SWOM} and $\phi$ is as in the proof of \Cref{DGSR46V}.
\end{lemma}
\begin{proof}
    We observe the restrictions 
    \begin{align*}
        \R_{\geq0}\times\{0\}\times X&\xrightarrow{\alpha_I\circ\phi}\R_{\geq0}\times X\\
        (t,0,x)&\mapsto \begin{cases}
            (t,I(t_x+t,q)), & x=I(t_x,q)\\
            (t,x), & x\in X\smallsetminus\Imm(I)
        \end{cases}
    \end{align*}
    and
    \begin{align*}
        \R_{\geq0}\times\R_{\geq0}\times\partial X&\xrightarrow{\alpha_I\circ \phi} \R_{\geq0} \times X\\
        (t,s,q)&\mapsto (t+s,I(t,q)).
    \end{align*}
    Both maps are the flow (for time $t$) along the vector field $V^+=\sum(\rho_U\circ\mrm{pr}_X)\cdot(\partial_s+V_U)$.
\end{proof}

@@

\begin{lemma}
    Suppose $U\subset C(Z)$ be conically smooth basics with $S_{C(Z)}\cong U$, and suppose that $U\cong C(L)$ is extendable. Let $\pi\colon \Link(C(Z))|_{U}\to U$ denote the link projection of $\Unzip (C(Z))$ over $U$. Then there is an isomorphism
    \[
        \partial\overline{\pi^{-1}U}\cong \Link_L(Z)
    \]
    and an induced conically smooth collar 
    \[
        (0,1]\times\partial\overline{\pi^{-1}U}\hookrightarrow \overline{\pi^{-1}U}
    \]
    which is a refinement onto its image.
\end{lemma}
\begin{proof}
    Up to isomorphism we have that $U=C^{<1}(L)\subset C^{<1}(Z)\subset C(Z)$ is induced by the inclusion $L=S_Z\subset Z$. Abbreviating $S=S_{C(Z)}$, the inclusion of $U$ factors as $U\subset S=C(L)$ . Now, using \Cref{7GBVGBA} we have $\Unzip C(Z)=\Unzip_{S}C(Z)=\R_{\geq0}\times\Unzip_L Z$ and so 
    \begin{align*}
        \Unzip C(Z)|_{U}&=\Link_{C(L)}C(Z)|_{C^{<1}(L)}\\
        &=\{0\}\times \Unzip_L Z\cup_{\{0\}\times\Link_LZ}[0,1)\times\Link_L Z\\
    \end{align*}
    since the projection $\pi\colon\Link_{C(L)}C(Z)=\{0\}\times\Unzip_L Z\cup_{\{0\}\times\Link_LZ}\R_{\geq0}\times \Link_L Z\to C(L)=\ast\amalg_{\{0\}\times L}\R_{\geq0}\times L$ is given by mapping all of $\{0\}\times\Unzip_L Z$ to $\ast$ and on $\R_{\geq0}\times \Link_LZ$ by $\id_{\R_{\geq0}}\times\pi'$ where $\pi'\colon \Link_LZ\to L$ is the link projection.
    Thus 
    \[
        \pi^{-1}\overline{U}=\pi^{-1}C^{\leq 1}(U)=\{0\}\times\Unzip_LZ\cup[0,1]\times\Link_LZ 
    \]
    and consequently 
    \[
        \pi^{-1}\partial\overline{U}=\pi^{-1}\{1\}\times L=\{1\}\times\Link_L Z,
    \]
    proving the first claim. The collar is immediate.
\end{proof}

>>>>

\documentclass[11pt]{amsart}

@@

\begin{lemma}\label{DYQ422D}
    Let $X$ be a smooth manifold with corners and let $I^+\colon\R_{\geq0}\times \partial(\R_{\geq0}\times\partial X)\hookrightarrow\R_{\geq0}\times X$ be as in \Cref{O6BEXS3}. Then 
    \[
        I^+=\alpha_I\circ\phi
    \]
    where $\alpha_I$ is as in \Cref{K52SWOM} and $\phi$ is as in the proof of \Cref{DGSR46V}.
\end{lemma}
\begin{proof}
    We observe the restrictions 
    \begin{align*}
        \R_{\geq0}\times\{0\}\times X&\xrightarrow{\alpha_I\circ\phi}\R_{\geq0}\times X\\
        (t,0,x)&\mapsto \begin{cases}
            (t,I(t_x+t,q)), & x=I(t_x,q)\\
            (t,x), & x\in X\smallsetminus\Imm(I)
        \end{cases}
    \end{align*}
    and
    \begin{align*}
        \R_{\geq0}\times\R_{\geq0}\times\partial X&\xrightarrow{\alpha_I\circ \phi} \R_{\geq0} \times X\\
        (t,s,q)&\mapsto (t+s,I(t,q)).
    \end{align*}
    Both maps are the flow (for time $t$) along the vector field $V^+=\sum(\rho_U\circ\mrm{pr}_X)\cdot(\partial_s+V_U)$.
\end{proof}

@@

\begin{lemma}\label{V6RIX5L}
    Let $L=S_Z$ and let $U=C^{<1}(L)\subset C^{<1}(Z)\subset C(Z)$. Let $\pi\colon \Link(C(Z))|_{U}\to U$ denote the link projection of $\Unzip (C(Z))$ over $U$. Then there is an isomorphism
    \[
        \partial\overline{\pi^{-1}U}\cong \Link_L(Z)
    \]
    and an induced conically smooth collar 
    \(
        (0,1]\times\partial\overline{\pi^{-1}U}\hookrightarrow \overline{\pi^{-1}U}
    \)
    which is a refinement onto its image.
\end{lemma}
\begin{proof}
    Using \Cref{7GBVGBA} we have $\Unzip C(Z)=\Unzip_{S}C(Z)=\R_{\geq0}\times\Unzip_L Z$ and so 
    \begin{align*}
        \Unzip C(Z)|_{U}&=\Link_{C(L)}C(Z)|_{C^{<1}(L)}\\
        &=\{0\}\times \Unzip_L Z\cup_{\{0\}\times\Link_LZ}[0,1)\times\Link_L Z\\
    \end{align*}
    since the projection $\pi\colon\Link_{C(L)}C(Z)=\{0\}\times\Unzip_L Z\cup_{\{0\}\times\Link_LZ}\R_{\geq0}\times \Link_L Z\to C(L)=\ast\amalg_{\{0\}\times L}\R_{\geq0}\times L$ is given by mapping all of $\{0\}\times\Unzip_L Z$ to $\ast$ and on $\R_{\geq0}\times \Link_LZ$ by $\id_{\R_{\geq0}}\times\pi'$ where $\pi'\colon \Link_LZ\to L$ is the link projection.
    Thus 
    \[
        \pi^{-1}\overline{U}=\pi^{-1}C^{\leq 1}(U)=\{0\}\times\Unzip_LZ\cup[0,1]\times\Link_LZ 
    \]
    and consequently 
    \begin{equation}\label{QX54WZB}
        \pi^{-1}\partial\overline{U}=\pi^{-1}\{1\}\times L=\{1\}\times\Link_L Z,
    \end{equation}
    proving the first claim. The collar is immediate.
\end{proof}

\begin{lemma}\label{FBLD2TE}
    Let $\R^n$ be equipped with a riemannian metric, and let $c\in\{0,\dots,n\}$. Then for any convex disk $D\subset\R^n$ about the origin the intersections
    \begin{enumerate}
        \item $D\cap (\R^{n-c}\times(\R^{c}\smallsetminus\R^{c}_{\geq0}))$
        \item $D \cap (\R^{n-c}\times\R^{c}_{>0})$
    \end{enumerate}
    are disks.
\end{lemma}
\begin{proof}

\end{proof}

\begin{proposition}
    Let $L=S_Z$ and let $I=J^+\colon \R_{\geq0}\times\Link_{C(L)}C(Z)\hookrightarrow\Unzip_{C(L)}C(Z)$ be the collar induced, according to \Cref{O6BEXS3}, by a collar $J\colon\R_{\geq0}\times\Link_L(Z)\hookrightarrow \Unzip_L(Z)$. Let $U$ be as in \Cref{V6RIX5L}, and let 
    \[
        p\in I(\{1\}\times\partial\overline{\pi^{-1}U}).
    \]
    Then:
    \begin{enumerate} 
        \item There is a diffeomorphism 
        \[
            \R_{>1}\times J(\R_{>0}\times\Link_LZ)\cap I([0,1]\times\overline{\pi^{-1}U})\cong (1,2]\times J((0,1]\times\Link_LZ)
        \]
        of smooth manifolds with corners.
        \item There exists a convex disk $D\subset\Unzip_{C(L)}C(Z)^\circ$ about $p$ such that $D\cap I([0,1)\times\pi^{-1}U)$ is a disk. 
        % \item There exists a chart neighbourhood $V\subset\Unzip_{C(L)}C(Z)^\circ$ of $p$ which is diffeomorphic to $\R_{>0}\times J(\R_{>0}\times W)$ where $W\subset\Link_L(Z)$ is the boundary of a chart neighbourhood in $\Unzip_LZ$.
        % \item There exists a homeomorphism 
        % \[
        %     \Psi\colon\R^2\times\Link_LZ\to \R_{>1}\times J(\R_{>0}\times\Link_LZ)
        % \]
        % such that 
        % \[
        %     \R_{>1}\times J(\R_{>0}\times\Link_LZ)\cap I([0,1]\times\overline{\pi^{-1}U})=\Psi(\R_{\leq0}^2\times\Link_LZ).
        % \]
    \end{enumerate}
\end{proposition}
\begin{proof}
    From the proof of \Cref{V6RIX5L} we recall that
    \(
        \overline{\pi^{-1}U}=\{0\}\times\Unzip_LZ\cup_{\{0\}\times\Link_LZ}[0,1]\times\Link_LZ.
    \)
    By \Cref{DYQ422D} we have $I=\alpha_J\circ\phi$, and observe that 
    \begin{align*}
        \phi([0,1]\times\overline{\pi^{-1}U})&= A'\cup B'\\
        &\coloneqq\bigcup_{t\in[0,1]}(X\subset X^{+t})\cup\{(t,q)\in X^{+(t+s)} : t,s\in[0,1]\}.
    \end{align*}
    Thus $I([0,1]\times\overline{\pi^{-1}U})=A\cup B\subset\Unzip_{C(L)}C(Z)=\R_{\geq0}\times\Unzip_LZ$ where $A=\alpha_J(A')$, $B=\alpha_J(B')$. We have 
    \begin{align*}
        &A=\{(r,x)\in\R_{\geq0}\times\Unzip_LZ : r\in[0,1],\ x\in \Unzip_LZ\smallsetminus J([0,r)\times\Link_LZ\}\\
        &B=\{(t+s,J(t,q))\in\R_{\geq0}\times\Unzip_LZ : t,s\in[0,1]\}
    \end{align*}
    and hence
    \[
        \R_{>1}\times J(\R_{>0}\times\Link_LZ)\cap(A\cup B)=\{(t+s,J(t,q)) : t\in(0,1],\ s\in[0,1],\ t+s>1\}
    \]
    as the intersection with $A$ is empty.

    Consider now the diffeomorphism 
    \begin{align*}
    \psi=\rho\circ\begin{pmatrix}
        1 & 1\\ 
        0 & 1
    \end{pmatrix}\circ\rho^{-1}\colon\R_{>1}\times\R_{>0}&\to\R_{>1}\times\R_{>0},\\
     (x,y)&\mapsto ((x-1)y+1,y)
    \end{align*} 
    where $\rho\colon\R^2\to\R_{>1}\times\R_{>0}$, $(x,y)\mapsto(e^x+1,e^y)$. Now $\psi$ fixes $(2,1)$ and satisfies 
    \[
        \psi((1,2]\times(0,1])=\{(t+s,t) : t\in(0,1],\ s\in[0,1],\ t+s>1\}.
    \] 
    Putting 
    \[
        \Psi=\id_{\R_{>1}}\times J\circ\psi\times\id_{\Link_LZ}\colon\R_{>1}\times\R_{>0}\times\Link_LZ\to\R_{>1}\times J(\R_{>0}\times\Link_LZ)
    \] 
    we obtain the map
    \begin{align*}
        (1,2]\times J((0,1]\times\Link_LZ)&\xrightarrow{\cong}(1,2]\times(0,1]\times\Link_LZ\\
        &\xrightarrow{\Psi|}\R_{>1}\times J(\R_{>0}\times\Link_LZ)\cap I([0,1]\times\overline{\pi^{-1}U}).
    \end{align*}
    The first map, which is a homeomorphism, is tautologically a diffeomorphism of smooth manifolds with corners with respect to the induced smooth structure on its target. With respect to the latter, $\Psi$ is a diffeomorphism as well. Hence the composition is a diffeomorphism. In particular, we obtain the restricted diffeomorphism
    \[
        (1,2)\times J((0,1)\times\Link_LZ)\cong\R_{>1}\times J(\R_{>0}\times\Link_LZ)\cap C_{U}.
    \]
    of smooth manifolds without boundary.

    Finally, consider $p=I(1,(1,q))=(2,J(1,q))$ where $q\in\Link_LZ$ (recall \eqref{QX54WZB}). Let $\R^{n-c}\times\R^{c}_{\geq0}\cong W\subset\Unzip_LZ$ be a chart neighbourhood of $q$. Without loss of generality we may assume $c=n$ for simplicity. Up to diffeomorphism we may write the restriction of the collar of $\Link_LZ$ as $J\colon\R_{\geq0}\times\partial\R^c_{\geq0})\hookrightarrow \R^c_{\geq0}$, given by the flow along the vector field $\sum_{1\leq i\leq c}\partial_i$ where $\{\partial_i\}$ is the standard basis of $\Tangent_0\R^c_{\geq0}$ (recall \Cref{O6BEXS3}). We now observe the diffeomorphism 
    \[
        J((0,1]\times\partial \R^{c}_{\geq0})=\R^c_{>0}\smallsetminus\left(\begin{pmatrix}
        1 \\ \vdots \\ 1
        \end{pmatrix}
        +\R^c_{\geq0}\right)
        \cong\R^c\smallsetminus\R^c_{>0}
    \]
    of smooth manifolds with corners.
    Consequently we have $(1,2]\times J((0,1]\times\partial\R^c_{\geq0})\cong\R^{c+1}\smallsetminus\R^{c+1}_{>0}$. These diffeomorphisms restrict to $J((0,1)\times \partial\R^c_{\geq0})\cong\R^c\smallsetminus\R^c_{\geq0}$ and so $(1,2)\times J((0,1)\times\partial\R^c_{\geq0})\cong \R^{c+1}\smallsetminus\R^{c+1}_{\geq0}$. Hence, the intersection of any convex disk $D\subset\R_{>1}\times J(\R_{>0}\times W)$ centred at $(2,J(1,q))=p$ with $I([0,1)\times\pi^{-1}U)$ is a disk by the first statement of \Cref{FBLD2TE}.
\end{proof}
